The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-08 ms.tex
abstract

\topmargin -1 cm
\defcitealias{WangMerritt:2004a}{WM04}

@@

\begin{document}
\title{Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

\begin{abstract}
We calculate steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  We derive analytic estimates for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.  These results (neglecting radiative cooling) are used to assess over what range of conditions radiative instability will develop, assuming an average star formation history for galaxies of the given black hole mass.  Our main conclusion is that.....  We briefly discuss implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies.
\end{abstract}

>>>>

\topmargin -1 cm

@@

\begin{document}
\title{The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes}
\maketitle

\begin{abstract}
We calculate steady-state, one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies for a range of black hole masses $M_{\bullet}$, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Analytic estimates are derived for quantities including the stagnation radius (where the radial velocity of the gas passes through zero) and the black hole accretion rate as a function of $M_{\bullet}$ and heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess over under conditions radiative instability will develop, based on the average star formation history for galaxies with a given black hole mass.  Our results for the average accretion rates, as well as the maximum thermally-stable and -unstable accreion rates, are compared to the measured nuclear X-ray luminosities of a sample of quiescent black holes, from which we conclude that...  We briefly discuss implications of our results for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies and the diversity of CNM environments encountered by the jetted outflows from tidal disruption events.
\end{abstract}
